Visitation_stacked_barplot

### 2021-03-15 Rmd/PPCA_Complete_Cases.Rmd
plots supplementary

#Load data
dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca.rds")
phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
dat_cleaning_5_nectar <- readRDS("Data/RData/data_subset_nectar.rds")
phyl_pca_forest_nectar <- readRDS("Data/RData/phyl_pca_forest_nectar_all.rds")
#CALL the output PC for simplicity
PC <- phyl_pca_forest
#CHECK CONTENT
#EIGENVALUES
PC$Eval
#PC score (POINTS)
PC$S
#PC loadings (ARROWS)
PC$L

@@

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
  dat$Nectar[dat$Nectar=="no"] <- "Absence"
   dat$Nectar <- factor(dat$Nectar, levels = c("Presence","Absence"))
  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Nectar),size=2)+scale_color_manual(values=c("grey", "black"))

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .75 * mult * (get(x)),
                      v2 = .75 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2),size=0.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")

@@

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.35,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,5,5,7,5.8,6.5)),
                          label = PCAloadings$Variables, color="black",size=5)

>>>>

#Load data
phyl_pca_forest_complete_cases <- readRDS("Data/RData/phyl_pca_forest_complete_cases.rds")
#CALL the output PC for simplicity
PC <- phyl_pca_forest_complete_cases
#CHECK CONTENT
#EIGENVALUES
PC$Eval
#PC score (POINTS)
PC$S
#PC loadings (ARROWS)
PC$L

@@

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density

  plot <- plot + geom_point(data=dat, aes(x, -y),size=2, colour="grey")

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .75 * mult * (get(x)),
                      v2 = .75 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=v1, yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=-v1, yend=v2),size=0.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.8, color="black")

@@

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,5.35,5,7.5,6.5,6)), y = -(PCAloadings$PC2*c(4.3,5,5,7,5.8,6.5)),
                          label = PCAloadings$Variables, color="black",size=5)

### 2021-03-15 Rmd/PPCA_Qualitative_Vars.Rmd
plots supplementary

#Load data
dat_cleaning_5 <- readRDS("Data/RData/Data_for_plotting_qualitative_pca_vars.rds")
phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")

@@

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.165, 0.1)) + ggtitle("D)")

@@

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.163, 0.115)) + ggtitle("F)")

@@

library(cowplot)
 plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Flower_sym(PC),Flower_sha(PC),Breeding_syst(PC), ncol=2,nrow=3,  align = "v")

>>>>

#Load data
dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca.rds")
phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")

@@

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.165, 0.1)) + ggtitle("F)")

@@

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.163, 0.115)) + ggtitle("D)")

@@

library(cowplot)
 plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC), ncol=2,nrow=3,  align = "v")

### 2021-03-15 Rmd/PPCA_Subset_Nectar.Rmd
plots supplementary

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=6, fig.width=16}

@@

#Load data
dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca.rds")
phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
dat_cleaning_5_nectar <- readRDS("Data/RData/data_subset_nectar.rds")
phyl_pca_forest_nectar <- readRDS("Data/RData/phyl_pca_forest_nectar_all.rds")
#CALL the output PC for simplicity
PC <- phyl_pca_forest
#CHECK CONTENT
#EIGENVALUES
PC$Eval
#PC score (POINTS)
PC$S
#PC loadings (ARROWS)
PC$L

#############################################################################################################################################################
#COMPATIBILITY
#############################################################################################################################################################
#Load plots
all_spp <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
  dat$Nectar[dat$Nectar=="no"] <- "Absence"
  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Nectar),size=2)+scale_color_manual(values=c("#fc2847", "#1cac78"))

  #ADD LABELS
  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.35,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,5,5,7,5.8,6.5)),
                          label = PCAloadings$Variables, color="black",size=5)

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.07, 0.11)) +ggtitle("")

#all_spp(PC)

@@

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$Nectar <- dat_cleaning_5_nectar$Nectar_presence_absence
  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
  dat$Nectar[dat$Nectar=="no"] <- "Absence"
  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Nectar),size=2)+scale_color_manual(values=c("#fc2847", "#1cac78"))
  # plot <- plot +geom_point(data=dat, aes(-x, -y, colour = density),size=0.65,shape = 1,colour = "black",alpha=0.8)

@@

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(6,5.35,5,6,6,6,6)), y = -(PCAloadings$PC2*c(5.75,5,4.75,5.75,5.8,5.5,6)),
                          label = PCAloadings$Variables, color="black",size=5)

@@

library(cowplot)
 plot_grid(all_spp(phyl_pca_forest),nectar_subset(phyl_pca_forest_nectar), ncol=2,  align = "h")

>>>>

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=8}

@@

#Load data
dat_cleaning_5_nectar <- readRDS("Data/RData/data_subset_nectar.rds")
phyl_pca_forest_nectar <- readRDS("Data/RData/phyl_pca_forest_nectar_all.rds")
#CALL the output PC for simplicity

@@

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$Nectar <- dat_cleaning_5_nectar$Nectar_presence_absence
  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
  dat$Nectar[dat$Nectar=="no"] <- "Absence"
  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Nectar),size=2)+scale_color_manual(values=c("grey", "black"))
  # plot <- plot +geom_point(data=dat, aes(-x, -y, colour = density),size=0.65,shape = 1,colour = "black",alpha=0.8)

@@

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(6,5.35,5.2,6,6,6,6)), y = -(PCAloadings$PC2*c(5.75,5,4.3,5.75,5.8,5.5,6)),
                          label = PCAloadings$Variables, color="black",size=5)

@@

nectar_subset(phyl_pca_forest_nectar)
